---
title: "Conclusion"
format:
  html: 
    toc: false
    link-external-icon: false
    link-external-newwindow: false
---

```{r include = FALSE}
source(here::here("R", "buttons.R"))
```

Congratulations! You've completed the *Add-On Packages* module!

## Learning Goals

Now that you've completing this module, you should be able to:

### Add-On Packages

1. Explain the procedure required to install, load, and use an R package
1. Install new R packages from a remote package repository
1. Load an R package
1. Use the functions provided by add-on packages

### Getting Help

1. Access the documentation for functions provided by installed packages
1. Explain the purpose of the sections in an R help file
1. Use the information in an R help file to learn how to use an unfamiliar R function

## Next Steps

If you want to continue with your R learning journey, we recommend following the *Matrices & Vectors* module next. Click
the button below to get started!.

```{r}
#| echo: false
#| results: asis

next_module_button("https://www.openstatprog.com/matrices-vectors/")
```
