---
title: "Conclusion"
format:
  html: 
    toc: false
    link-external-icon: false
    link-external-newwindow: false
---

```{r include = FALSE}
source(here::here("R", "buttons.R"))
```

Congratulations! You've completed the *First Steps* module!

## Hand-In Assignment

::: practice

## Hand in Assignment

This assignment can be used as part of a course. Through this assignment, you show that you understand everything covered in this module: basic commands, functions, packages, and documentation.
Complete each step below in your own R session, then submit your work (see "What to Hand In" below).

1. **Basic Commands.** Create an object called `weekly_spend` containing at least five numeric values, representing
   a week's worth of daily spending (in whatever currency you like). Then create a second object called
   `over_budget` that uses a logical comparison to check whether the *average* daily spend in `weekly_spend` exceeds
   20.
1. **Functions.** Using two *different* built-in functions, calculate (a) the total of `weekly_spend` and (b) the
   average of `weekly_spend`. Store each result in its own, sensibly-named object.
1. **Packages.** Install and load the **scales** package. Use the `scales::dollar()` function it provides to format
   your total from step 2 as currency (e.g., `"$142.50"`).
1. **Documentation.** Open the help file for one function you have *not* used anywhere in this module (your choice —
   `sd()`, `median()`, and `range()` are all good candidates, but any function is fine). In a comment in your script,
   write one sentence explaining what the function does and a plausible reason you might use it.

### What to Hand In

Save all of your commands, in the order you ran them, in a single plain-text or R script file (e.g.
`yourname_first-steps.R`). Include your comment from step 4 directly in that file.

A teacher reviewing your submission should be able to read straight through your script and see: the objects you
created, the functions you called and why, evidence that you installed and loaded a package, and your one-sentence
explanation of an unfamiliar function.

:::

## Learning Goals

Now that you've completing this module, you should be able to:

### Basic Commands

1. Create simple R objects
1. Conduct simple mathematical calculations involving R objects
1. Conduct simple logical comparisons between R objects

### R Functions

1. Recognize the R functions in a section of R code
1. Give a conceptual overview of how R functions operate
1. Call R functions to perform calculations on R objects

### Add-On Packages

1. Explain the procedure required to install, load, and use an R package
1. Install new R packages from a remote package repository
1. Load an R package
1. Use the functions provided by add-on packages

### Getting Help

1. Access the documentation for functions provided by installed packages
1. Explain the purpose of the sections in an R help file
1. Use the information in an R help file to learn how to use an unfamiliar R function

## Next Steps

If you want to continue with your R learning journey, we recommend following the *Data Types* module next. Click the 
button below to start the next module.

```{r}
#| echo: false
#| results: asis

next_module_button("https://www.openstatprog.com/data-types/index.html")
```
