---
title: "Add-On Packages"
page-navigation: false
format:
  html: 
    toc: false
---

```{r, echo = FALSE, include = FALSE}
source(here::here("R", "buttons.R"))
```

::: {.column-margin}

:::: completion-time

**About 45–60 minutes**, including practice exercises and knowledge quizzes.

::::

:::

Welcome to the *Add-On Packages* module. In this module, you will learn how to use supplementary software packages that
greatly extend R's core functionality. This module is divided into two tutorials.

1. [R Packages](/tutorials/packages/index.qmd)
1. [Documentation](/tutorials/help/index.qmd)

Each tutorial will comprise a series of interactive lessons with practice problems embedded throughout. After you
complete each tutorial, you will have the opportunity to complete a knowledge quiz to check your learning.

## Learning Goals

After completing this module, you will be able to:

### R Packages

1. Explain the procedure required to install, load, and use an R package
1. Install new R packages from a remote package repository
1. Load an R package
1. Use the functions provided by add-on packages

### Documentation

1. Access the documentation for functions provided by installed packages
1. Explain the purpose of the sections in an R help file
1. Use the information in an R help file to learn how to use an unfamiliar R function

Click the button below to get started!

```{r}
#| echo: false
#| results: asis
begin_button("/tutorials/packages/index.qmd")
```
