---
title: "Accessing Help Files"
webr:
  packages:
    - dplyr
  autoload-packages: false
---

The simplest way to access a function's help file is to prepend the function name (without parentheses) with the `?`
character. For example, the following code will pull up the documentation for the `lm()` function.

::: {.column-margin}

:::: reading

[R4DS 8: Getting Help](https://r4ds.hadley.nz/workflow-help.html)

::::

:::

**Do:** Run the following code to open the help file for the `lm()` function.

```{webr-r}
?lm
```

You can achieve the same effect by providing the function name to the `help()` function.

```{r}
#| eval: false

help(lm)
help("lm")
```

A function's help file comes from the package that provides the function. So, you typically cannot access the help file
for a function until you've loaded the package that provides that function.

**Do:** Run the following code, and take note of the results. What went wrong?


```{webr-r}
?arrange
```

::: explanation

The code will produces an error because we're trying to access the documentation for `arrange()`, but we haven't yet
loaded the **dplyr** package that provides the `arrange()` function.

:::

We can still access the help files for functions provided by an unloaded package, though. We just have to tell R which
package provides the function (and, hence, where to look for the help file). To do so, either use the *namespace
resolution operator*, `::`, or provide a value for the `package` argument in the `help()` function.

**Do:** Run the following two code chunks. Why do these commands run successfully?

```{webr-r}
?dplyr::arrange
```

```{webr-r}
help(arrange, package = "dplyr")
```

::: explanation

Both commands run without errors, because we've told R to search for the `arrange()` documentation in the **dplyr**
package

:::

::: practice

Access the help file for the `vector()` function.

1. How many arguments does the `vector()` function take?
1. What is the default value of the `mode` argument?

:::: {.panel-tabset}

## {{< var tab_title.editor >}}

```{webr-r}
```

## {{< var tab_title.hint >}}

The `vector()` function is provided by the **base** package, which is loaded every time you start R. So, you should be
able to access the help file without loading any additional packages.

## {{< var tab_title.solution >}}

According to the *Usage* section of `vector()`'s documentation,

1. The `vector()` function takes 2 arguments: `mode` and `length`.
1. The default argument for `mode` is "logical".

```{r, echo = FALSE, include = FALSE}
library(printr)
```

```{r}
?vector
```

::::

:::

::: knowledge-check

- What are two ways to open a function's help file?
- If you get an error opening a help file with `?some_function`, what's one possible reason?

```{webr-r}
```

:::
