---
title: "Independent Task"
knitr:
  opts_chunk:
    cache: false
---

```{r setup, echo = FALSE, include = FALSE}
library(printr)
```

You've now practiced opening help files, reading their sections, and using them to figure out argument order and default
values, with some guidance along the way. This page works the same muscle, but without the step-by-step scaffolding.
You're on your own this time, the same way you will be when you encounter an unfamiliar function in your own work.

::: practice

The `strsplit()` function is part of Base R, so it's available without loading any additional packages. You haven't
used it anywhere in this module. Using only its help file, answer the following questions.

:::: {.panel-tabset}

## {{< var tab_title.question >}}

1. Provide a one-sentence description of what `strsplit()` does.
1. What are the argument names; in what order are the arguments specified?
1. What arguments have default values, and what are those values?

## {{< var tab_title.solution >}}

```{r}
?strsplit
```

1. `strsplit()` uses a pattern matching to split a character vector into substrings.
1. The arguments are `x`, `split`, `fixed`, `perl`, and `useBytes`, specified in that order.
1. `fixed`, `perl`, and `useBytes` all default to `FALSE`.

::::

:::

::: practice

Write a function call that splits the text `"apple,banana,cherry"` into the three individual words: `"apple"`, `"banana"`,
`"cherry"`.

:::: {.panel-tabset}

## {{< var tab_title.editor >}}

```{webr-r}
"apple,banana,cherry"
```

## {{< var tab_title.solution >}}

```{r}
strsplit("apple,banana,cherry", split = ",")
```

::::

:::

::: {.callout-tip}

## Ready to Continue?

You're ready to progress if you can:

- Explain why documentation is useful, even for functions you already know how to call.
- Open a function's help file, whether or not the providing package is already loaded.
- Identify the *Description*, *Usage*, *Arguments*, *Details*, *Value*, and *Examples* sections of a help file, and
explain what each contains.
- Use a help file to find the information that you need to correctly call a function you've never used before.

Take the [Knowledge Quiz](/quizzes/help/index.qmd) to evaluate your learning.

:::
