---
title: "Independent Task"
knitr:
  opts_chunk:
    cache: false
---

```{r setup, echo = FALSE, include = FALSE}
library(printr)
```

You've now practiced opening help files, reading their sections, and using them to figure out argument order and
default values with some guidance along the way. This page works the same muscle, but without the step-by-step
scaffolding. You're on your own this time, the same way you would be when you encounter an unfamiliar function in
your own work.

::: practice

## Independent Task

The `strsplit()` function is part of Base R, so it's available without loading any additional packages. You haven't
used it anywhere in this module. Using only its help file, answer the following:

1. What does `strsplit()` do, in one sentence?
1. What are its arguments called, and in what order are they specified?
1. Does any argument have a default value? If so, what is it?
1. Write a function call that splits the text `"apple,banana,cherry"` into its three individual words, using the
   comma as the split point.

:::: {.panel-tabset}
## {{< var tab_title.question >}}

Open `strsplit()`'s help file however you'd like, and work through the four questions above before checking the
solution.

## {{< var tab_title.solution >}}

```{r}
?strsplit
```

1. `strsplit()` splits the elements of a character vector into substrings, according to a specified splitting
   character or pattern.
1. Its arguments are `x`, `split`, `fixed`, `perl`, and `useBytes`, specified in that order.
1. `fixed`, `perl`, and `useBytes` all default to `FALSE`. `x` and `split` have no defaults — you must supply them.
1.
   ```{r}
   strsplit("apple,banana,cherry", split = ",")
   ```
::::

:::

::: {.callout-tip}

## Ready to Continue?

You've now completed the *Documentation* tutorial. You're ready to move on if you can:

- Explain why documentation matters, even for functions you already know how to call.
- Open a function's help file, whether or not the providing package is already loaded.
- Identify the *Usage*, *Arguments*, and *Examples* sections of a help file, and explain what each contains.
- Use a help file to correctly call a function you've never used before, entirely on your own.

If any of these still feel shaky, revisit the relevant page above, or try the
[Knowledge Quiz](/quizzes/help/index.qmd) to pinpoint exactly where to focus. Once you're ready, head to the
[Conclusion](/conclusion.qmd) page to find this module's hand-in assignment.

:::
