---
title: "Help File Sections"
webr:
  packages:
    - dplyr
---

```{r setup, echo = FALSE, include = FALSE}
library(printr)
```

R help files can contain diverse information: some are only a few lines long while others contain dozens of pages of 
information. Not all R help files include all possible sections, but there are a few core sections that tend to show up
pretty consistently due to their general usefulness. Below, we'll walk through those sections using the documentation
for the `arrange()` function (from the **dplyr** package) as a concrete example.

## Description 

```{=html}

{{< include /assets/docs/arrange_description.html >}}

```

As the name implies, the *Description* section provides a brief, human-readable description of the functions purpose.

## Usage

```{=html}

{{< include /assets/docs/arrange_usage.html >}}

```

The *Usage* section shows the fully parameterized function call. In other words, how to call the function. In particular,
this section provides several crucial pieces of information.

- The name used to call the function
- The name of all the function arguments
- The order of the function arguments
- Any default values defined for function arguments

## Arguments

::: {.column-margin}

:::: {.callout-note}

The *Usage* and *Arguments* sections will
probably be the ones you reference most frequently. These two sections provide all the information you'll need to use
most functions.

::::

:::

```{=html}

{{< include /assets/docs/arrange_arguments.html >}}

```

The *Arguments* section briefly explains each function argument. This section explains the purpose of each function
argument and what type of values you are able to specify for each argument.

## Details

```{=html}

{{< include /assets/docs/arrange_details.html >}}

```

The *Details* section expands on the information listed in the *Arguments* section to provide additional details of
function arguments or the function's behavior

## Value

```{=html}

{{< include /assets/docs/arrange_value.html >}}

```

The *Value* section describes the type of object returned by the function.

## Examples

```{=html}

{{< include /assets/docs/arrange_examples.html >}}

```

The *Examples* section contains executable R code that demonstrates the function's primary use-cases.

::: practice

## Practice

Run the first line of example code from the *Examples* section of the `arrange()` documentation shown above.

:::: {.panel-tabset}

## {{< var tab_title.editor >}}

```{webr-r}
```

## {{< var tab_title.hint >}}

You can copy and paste the code directly from the examples section into the editor window.

## {{< var tab_title.solution >}}

```{r}
library(dplyr)

arrange(mtcars, cyl, disp)
```
::::

:::

::: knowledge-check

Which section of the help file would you check to find the following information.

- A function's default argument values?
- A short, plain-language summary of what a function does?
- Working example code that you can copy and adapt?

:::
