---
title: "Installing Packages"
knitr:
  opts_chunk:
    eval: false
---

R packages are just little pieces of software, so you can think about installing R packages just like you'd think about
installing any other piece of software. Installing a package is something you only need to do **once** per computer
(much like you only needed to install R once).

To install a new package, we'll typically use the `install.packages()` function. In most cases, you only need to specify
the package's name as a character string. For example, the following code installs the **psych** package.

```{r}
# Install one package
install.packages("psych")
```

If you want to install more than one package in a single `install.packages()` call, use the `c()` function to combine
several package names into a single call (don't forget to quote each name). Below, we're installing the **mice** and
**lavaan** packages.

```{r}
# Install two packages
install.packages(c("mice", "lavaan"))
```

That's it: those two patterns cover almost all the package installs you'll ever need to do. Pretty simple, right?

::: common-mistakes

A few things commonly trip people up when they try to install a package.

**Mistake 1:** Misspelling the package name

```{r}
#| eval: false

install.packages("ggplot")
```

```{r}
#| eval: true
#| echo: false
#| error: true
#| warning: true

install.packages("ggplot", lib = "~/")
```

The code above fails because the package is actually called `ggplot2`. R can't guess what package you want, so the
install fails. If you see this error, double-check the spelling of the packages name.

**Mistake 2:** Forgetting to quote the package name

```{r}
#| eval: true
#| error: true
#| warning: true

install.packages(psych)
```

 In the above code, we don't quote the package name, so R looks for an *object* called `psych` in which it will try to
 find a character string naming a package. There's no object call `psych` in our environment, so search fails which
 causes the install to fail. Package names passed to `install.packages()` must be character strings: don't forget the
 quotes!

**Mistake 3:** No internet connection

`install.packages()` needs to download the package from the internet. So, if you're offline, the install will fail with
a fairly cryptic error message like the one shown below.

```
Warning: unable to access index for repository https://cran.rstudio.com/src/contrib:
  cannot open URL 'https://cran.rstudio.com/src/contrib/PACKAGES'
Warning: unable to access index for repository https://cran.rstudio.com/src/contrib:
  cannot open URL 'https://cran.rstudio.com/src/contrib/PACKAGES'
Warning message:
package ‘mice’ is not available for this version of R

A version of this package for your version of R might be available elsewhere,
see the ideas at
https://cran.r-project.org/doc/manuals/r-patched/R-admin.html#Installing-packages 
```

:::

::: practice

## Practice

Use the `install.packages()` function to install the following packages.

- `ggplot2`
- `dplyr`
- `haven`

:::: {.panel-tabset}

## {{< var tab_title.editor >}}

```{webr-r}
```

## {{< var tab_title.solution >}}

```{r}
install.packages(c("ggplot2", "dplyr", "haven"))
```

::::

:::

::: going-further

Everything above covers what you need for day-to-day R usage. This box covers a few more advanced topics that may come
in handy as you progress in your R journey. You don't need to master these ideas now.

### CRAN Mirrors

By default, `install.packages()` downloads packages from the *Comprehensive R Archive Network* (CRAN): a global network
of servers ("mirrors") that each host a complete copy of all published R packages. RStudio automatically picks a
sensible default mirror, so you don't normally need to specify one. If you ever want to select a particular CRAN mirror,
you can do so via the `repos` argument.

```{r}
# Explicitly specify a CRAN mirror
install.packages(c("lattice", "gridExtra"), repos = "https://cloud.r-project.org")
```

### Alternative Repositories

Occasionally, a package you need lives outside CRAN. Some other popular repositories include
[Bioconductor](https://www.bioconductor.org/packages/release/BiocViews.html#___Software) (specialized bioinformatics
packages) and [R-Universe](https://r-universe.dev/search).

### Installing Development Versions

Package developers often share in-progress work on code-hosting platforms like [GitHub](https://github.com). A package's
development version may have new features or bug fixes that are not yet available in the production version released
through CRAN. The [**remotes**](https://cran.r-project.org/web/packages/remotes/index.html) package lets you install an
R package directly from a GitHub repository.

```{r}
# Install the development version of the mice package from GitHub
remotes::install_github("amices/mice")
```

### Installing in a Non-Standard Location

Typically, R will automatically choose the location in which to install packages and prompt you if it needs to use a
different location (e.g. because you lack write permissions for the original location). To see a list of all the
locations where R will try to install packages, run the `.libPaths()` function.

```{r}
.libPaths()
```

```
[1] "/home/alice/R/library/4.5"  "/home/alice/R/ide/4.5"
[3] "/opt/R/4.5.3/lib/R/library"
```

If you know that you want to install a package outside the normal location (e.g., because your employer doesn't allow
you to install software outside of your user's home directory), you can explicitly specify the installation directory
with the `lib` argument.

```{r}
# Install the mvtnorm package into a specific, non-default directory
install.packages("mvtnorm", lib = "~/software/r_packages")
```

:::
