---
title: "Installing Packages"
knitr:
  opts_chunk:
    eval: false
---

Installing a package is something you only need to do **once** per computer (much like installing RStudio itself
only once). In most cases, you only need to give the package's name to the `install.packages()` function. The
following code installs the **psych** package.

```{r}
## Install one package
install.packages("psych")
```

If you want to install more than one package at once, use the `c()` function to combine several package names into a
single call.

```{r}
## Install two packages at once
install.packages(c("mice", "lavaan"))
```

That's it — those two patterns cover the vast majority of package installs you'll ever need to do.

## Common Errors

A few things commonly trip people up the first time they install a package:

- **Misspelling the package name.** `install.packages("ggplot")` (missing the `2`) will fail, because the package is
  actually called `ggplot2`. R can't guess what you meant, so double-check the spelling against the package's
  documentation or CRAN page.
- **Forgetting the quotes.** `install.packages(psych)` (without quotes) tells R to look for an *object* called
  `psych`, not a package name, and will produce an error. Package names passed to `install.packages()` must be
  character strings, wrapped in quotes.
- **No internet connection.** `install.packages()` needs to download the package, so it will fail (often with a
  fairly cryptic error) if you're offline.

::: practice

## Practice

Use the `install.packages()` function to install the following packages in the default location.

- `ggplot2`
- `dplyr`
- `haven`

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}
```

## {{< var tab_title.solution >}}

```{r}
install.packages(c("ggplot2", "dplyr", "haven"))
```
::::

:::

::: {.callout-note}

## Optional / Going Further: Repositories, Development Versions, and Library Locations

Everything above covers what you need for day-to-day work. This box covers a few more advanced topics you can come back to later if you ever need them.

**Where packages come from.** By default, `install.packages()` downloads packages from the *Comprehensive R Archive
Network* (CRAN). This is a global network of servers ("mirrors") that each host a complete copy of all published R packages.RStudio automatically picks a sensible default mirror, so you don't normally need to specify one. If you ever want to set one explicitly, you can do so via the `repos` argument.

```{r}
## Explicitly specify a CRAN mirror
install.packages(c("lattice", "gridExtra"), repos = "https://cloud.r-project.org")
```

**Other repositories.** Occasionally, a package you need lives outside CRAN. Some other popular repositories include
[Bioconductor](https://www.bioconductor.org/packages/release/BiocViews.html#___Software) (specialized bioinformatics
packages) and [R-Universe](https://r-universe.dev/search).

**Installing development versions.** Package developers often share in-progress work on code-hosting platforms like
[GitHub](https://github.com). The [**remotes**](https://cran.r-project.org/web/packages/remotes/index.html) package
lets you install directly from a GitHub repository, which sometimes gets you bug fixes or new features before they
reach CRAN.

```{r}
## Install the development version of the mice package from GitHub
remotes::install_github("amices/mice")
```

**Choosing a library location.** R usually figures out on its own where to install packages, prompting you if it
needs a different location (e.g. because you lack write permission somewhere). You can also specify this explicitly
with the `lib` argument.

```{r}
## Install into a specific, non-default directory
install.packages("mvtnorm", lib = "../software")
```

:::
