---
title: "Loading Packages"
webr:
  packages:
    - ggplot2
knitr:
  opts_chunk:
    eval: false
---

Once you've installed a package, you're nearly ready to use its functions, but there's still one step left: you
must *load* the package into your active R session.

The following code produces an error because we're trying to use the `ggplot()`, `aes()`, and `geom_boxplot()`
functions provided by the **ggplot2** package, without having loaded that package first.

```{r, eval = TRUE, error = TRUE}
ggplot(iris, aes(Species, Petal.Length)) + geom_boxplot()
```

An R package is really just a small piece of software. Like any other software, you only need to *install* it once
(just like you only need to install RStudio once), but you need to *load* it every time you start a new R session and
want to use it (just like you need to open RStudio every time you want to use it).

We load packages with the `library()` function.

```{r}
library(dplyr)
```

`library()` can only load one package at a time, so call it once per package if you need more than one.

```{r}
library(dplyr)
library(ggplot2)
```

Running the code below should now produce a simple plot, since we've loaded **ggplot2** before trying to use the
functions it provides.

```{webr-r}
library(ggplot2)

ggplot(iris, aes(Species, Petal.Length)) + geom_boxplot()
```

## Common Errors

- **Using a package's functions before loading it.** This is exactly the error you saw at the top of this page.
  It's the single most common package-related mistake. If R tells you it "could not find function," check whether
  you've loaded the package that provides it.
- **Trying to load a package you haven't installed.** `library()` will error with something like "there is no
  package called..." if the package isn't installed yet. Installing and loading are two separate steps. You need to
  install a package (once) before you can ever load it.
- **Misspelling or mis-capitalizing the package name.** Package names are case-sensitive, just like function names.
  `library(Dplyr)` will fail even though `library(dplyr)` works fine.

## Quick Check

- What's the difference between *installing* a package and *loading* a package?
- If R says `could not find function "arrange"`, what's the most likely fix?

```{webr-r}
```

::: {.callout-tip}

## Ready to Continue?

You're ready to move on to [Documentation](/tutorials/help/index.qmd) if you can:

- Explain the difference between installing and loading a package.
- Install a new package using `install.packages()`.
- Load an installed package using `library()`.
- Recognize the error you get when you try to use a function from a package you haven't loaded.

If any of these still feel shaky, revisit the relevant page above, or try the
[Knowledge Quiz](/quizzes/packages/index.qmd) to pinpoint exactly where to focus.

:::
