---
title: "Loading Packages"
webr:
  packages:
    - ggplot2
  autoload-packages: false
knitr:
  opts_chunk:
    eval: false
---

Once you've installed a package, you're nearly ready to use its functions, but there's still one step left: you must
*load* the package into your active R session.

**Do:** Run the following code, and take note of the results.

```{webr-r}
ggplot(iris, aes(Species, Petal.Length)) + geom_boxplot()
```

**See:** The code produces an error because we're trying to use the `ggplot()`, `aes()`, and `geom_boxplot()` functions
provided by the **ggplot2** package, without having loaded that package first.

An R package is really just a small piece of software. Like any other software, you only need to *install* a package
once (just like you only needed to install RStudio once), but you need to *load* a package every time you want to use it
in a new R session (just like you need to open RStudio every time you want to use it).

We load packages with the `library()` function.

```{r}
# Load the dplyr package
library(dplyr)
```

The `library()` function can only load one package at a time. So, you need one `library()` call for every package that
you want to load.

```{r}
# Load the dplyr and ggplot2 packages
library(dplyr)
library(ggplot2)
```

**Do:** Run the code below, and note how the results differ from the previous attempt.

```{webr-r}
library(ggplot2)

ggplot(iris, aes(Species, Petal.Length)) + geom_boxplot()
```

**See:** You should now see a simple plot. Since we've loaded **ggplot2** before trying to use the functions it
provides, our code executes successfully.

::: common-mistakes

**Mistake 1:** Using a package's functions before loading the package

This is the error you saw at the top of this page, and it's probably the single most common package-related mistake. If
R tells you it "could not find function...", check whether you've loaded the package that provides that function.

**Mistake 2:** Trying to load a package you haven't installed

```{r}
#| eval: true
#| error: true

library(tensor)
```

In the code above, `library()` errors because we haven't installed the **tensor** package. Remember that installing and
loading are two separate steps. You need to install a package (once) before you can load that package.

**Mistake 3:** Misspelling or mis-capitalizing the package name

R can't guess the package you wanted to load if you misspell the package's name.

```{r}
#| eval: true
#| error: true

library(gggplot2)
```

Likewise, package names are case-sensitive, just like everything else in R.

```{r}
#| eval: true
#| error: true

library(ggPlot2)
```

:::

::: knowledge-check

- What is the difference between *installing* a package and *loading* a package?
- If R says `could not find function "arrange"`, what is the most likely fix?

```{webr-r}
```

:::

::: {.callout-tip}

## Ready to Continue?

You're ready to move on to [Documentation](/tutorials/help/index.qmd) if you can:

- Explain the difference between installing and loading a package.
- Install a new package using `install.packages()`.
- Load an installed package using `library()`.
- Recognize the error you get when you try to use a function from a package you haven't loaded.

Take the [Knowledge Quiz](/quizzes/packages/index.qmd) to evaluate your learning.

:::
